Quality measure notes

### 2021-07-24 StateOfPractice/Ao-Report/14MeasurementResults.tex
MI report - minor updates

We considered anyone who made at least one accepted commit to the source code as a contributor. Thus, it does not mean that any development teams had long-term members as many as 100. Many of these projects received change requests and code from the community, such as pull requests and git commits on GitHub.

@@

We failed installing \textit{DICOM Viewer}, so we could not test \textit{surface reliability} and \textit{surface robustness} for it. We might underestimate the scores of the two qualities for this software. We kept this software on our list because the other seven qualities do not rely on a successful installation. Besides, it used a unique dependency, and we wanted to keep the diversity.

@@

We identified five projects using continuous integration and continuous delivery (CI/CD) tools, which are \textit{3D Slicer}, \textit{ImageJ
}, \textit{Fiji}, \textit{dwv}, and \textit{OHIF Viewer}.

@@

The top software products had higher scores in most criteria. For example, \textit{3D Slicer} ranked in the top two software products for all qualities except \textit{surface robustness}; \textit{ImageJ} ranked in the top three products for \textit{correctness \& verifiability}, \textit{surface reliability}, \textit{surface usability}, \textit{maintainability}, \textit{ surface understandability}, and \textit{visibility/transparency}; \textit{OHIF Viewer} ranked in the top five products for \textit{correctness \& verifiability}, \textit{surface reliability}, \textit{surface usability}, \textit{maintainability}, and \textit{reusability}. We might underestimate its scores of two qualities for \textit{DICOM Viewer}, but equally compared it with the other software for the rest seven qualities.

>>>>

We considered anyone who made at least one accepted commit to the source code as a contributor. Thus, it does not mean that any development team has are 100 long-term members. Many of these projects received change requests and code from the community, such as pull requests and git commits on GitHub.

@@

We failed installing \textit{DICOM Viewer}, so we could not test \textit{surface reliability} and \textit{surface robustness} for it. We kept this software on our list because the other seven qualities do not rely on a successful installation. Besides, it used a unique dependency, and we wanted to keep the diversity.

@@

We identified five projects using CI/CD tools, which are \textit{3D Slicer}, \textit{ImageJ
}, \textit{Fiji}, \textit{dwv}, and \textit{OHIF Viewer}.

@@

The top three software products \textit{3D Slicer}, \textit{ImageJ}, and \textit{OHIF Viewer} had higher scores in most criteria. \textit{3D Slicer} ranked in the top two software products for all qualities except \textit{surface robustness}; \textit{ImageJ} ranked in the top three products for \textit{correctness \& verifiability}, \textit{surface reliability}, \textit{surface usability}, \textit{maintainability}, \textit{ surface understandability}, and \textit{visibility/transparency}; \textit{OHIF Viewer} ranked in the top five products for \textit{correctness \& verifiability}, \textit{surface reliability}, \textit{surface usability}, \textit{maintainability}, and \textit{reusability}. We might underestimate its scores of qualities \textit{surface reliability} and \textit{surface robustness} for \textit{DICOM Viewer}, but equally compared it with the other software for the rest seven qualities.
